### 2024-07-08 research-methods.qmd
20240707 - interval/ratio

- temperature on the Kelvin scale
- height
- weight
- age
- distance
- speed
- volume
- time elapsed
- income
- years of formal education
- points in football

>>>>

- temperature on the Kelvin scale
- height
- weight
- age
- distance
- speed
- volume
- time elapsed
- income
- stock price
- years of formal education
- points in football
